The evolution of gene expression in the term placenta of viviparous mammals

### 2016-04-04 manuscript/manuscript.Rnw
add funding support

>>>>

  \section*{Funding}
  Partial support for this research came from the \textit{Eunice
    Kennedy Shriver} National Institute of Child Health and Human
  Development (NICHD), National Institutes of Health, U.S. Department
  of Health and Human Services (N01-HD-3342), and the National Science
  Foundation BCS-0827546.
